Joint Power Allocation and Network Slicing in an End-to-End O-RAN System

### 2019-10-28 Latex/tex/pr.tex
last version for figures1

Based on their type of request, UEs are classified into various services where UEs in the same service has similar service requests. In addition, each service is mapped to one or more slices based on the resource of the slices. Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center. For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.

@@

&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\

@@

\eqref{c11} and \eqref{c12} indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.

@@

@@

Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

@@

&+\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{d_{(s,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\

@@

p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+

>>>>

Based on their type of request, UEs are classified into various services where UEs in the same service has similar service requests. In addition, each service is mapped to one or more slices based on the resource of the slices. Each VNF of the O-RAN is mapped to one or some virtual machines (VMs) in the data center. For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.

@@

&  p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\
&  p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,\label{c122} \\

@@

\eqref{c11}, \eqref{c12} and \eqref{c122} indicate that the power of each RU do not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE do not exceed maximum power, respectively. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.

@@

&  p_{u_{(v,k)}}  \leq P_{max}^U  &&\quad \forall v, \forall k,  \\

@@

Assume $\boldsymbol{\lambda}$, $\boldsymbol{\chi}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

@@

&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
&-\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \chi_{u_{(v,k)}} (p_{u_{(v,k)}}  - P_{max}^U)\\

@@

p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }-\chi_{u_{(v,k)}}]^+
